PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Update on Overleaf.

That being said, in 2015, the Google DeepMind team demonstrated how a convolutional
recurrent neural network could learn to play the game Break-Out (amongst
48 other Atari games) by only looking at the gaming console
screen~\cite{mnih2015human}. This result represents a major milestone: they showede
that a relatively small sample size (about 500 games) is sufficient for an 
artificial agent to not only learn how to play (which requires an implicit model 
of time to adequately move the Break-Out paddle), but to also create gaming 
strategies that look like they would necessitate planning (the system first
breaks bricks on one side to eventually get the ball to break-out and reach out the area
above the remaining bricks, therefore ensuring rapid progress in the
game).

>>>>

That being said, in 2015, the Google DeepMind team demonstrated how a convolutional
recurrent neural network could learn to play the game Break-Out (amongst
48 other Atari games) by only looking at the gaming console
screen~\cite{mnih2015human}. This result represents a major milestone: they showed
that a relatively small sample size (about 500 games) is sufficient for an 
artificial agent to not only learn how to play (which requires an implicit model 
of time to adequately move the Break-Out paddle), but to also create gaming 
strategies that look like they would necessitate planning (the system first
breaks bricks on one side to eventually get the ball to break-out and reach out the area
above the remaining bricks, therefore ensuring rapid progress in the
game).
